The Local Group in the Cosmic Web

### 2014-10-14 paper/main.tex
starting to update some references

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

\begin{document}

\title{The Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

@@

Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
product between angular momentum of the  two halos. We find a a slight
alignment of spin vectors for the $2\sigma$ sample with a median around
$|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
alignment with the orbital angular momentum nor the cosmic web. This
is also consistent with recent results that show that the spin
alignment of halos of masses around $10^{12}$\Msun is very weak
\citep{ForeroRomero2014}.

@@

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

\begin{document}
 %@arxiver{fig1.pdf,fig3c.pdf,fig4c.pdf,fig5.pdf}

\title{The Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}
\email{regonzar@astro.puc.cl}

@@

Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
product between angular momentum of the  two halos. We find a a slight
alignment of spin vectors for the $2\sigma$ sample with a median around
$|\mu|\sim 0.7$ ($45$ degrees) which is barely above the no-alignment expectation marked by the shaded region. Furthermore, we found no significant
alignment with the pair orbital angular momentum nor the cosmic web. This
absense of alignment consistent with recent results that show that the spin
alignment of halos of masses around $10^{12}$\Msun is very weak
\citep{ForeroRomero2014}.

@@

Codis->spin
http://adsabs.harvard.edu/abs/2012MNRAS.427.3320C

I've just read the pre-print you had on the arXiv today (The Local Group in the Cosmic Web). You make some interesting comments about the distribution of the LG galaxies and their satellites, i.e. about a joint consideration of the MW-M31 orientation and their satellite systems. You might find it interesting that I have been working on this issue a lot lately (see in particular Pawlowski, Kroupa & Jerjen, 2013, MNRAS, 435, 1928 and Pawlowski & McGaugh, 2014, MNRAS, 440, 908). In addition to the satellite planes (VPOS around the MW, GPoA around M31), the more-distant dwarf galaxies in the LG are part of coherent and surprisingly symmetric structures, too.

Concerning the idea that the distribution of satellite galaxies is shaped by the accretion of sub-halos along filaments, I'd like to point out that this effect is not strong enough to explain the observed, very narrow and coherent satellite structures (e.g. the recent Pawlowski et al. 2014, MNRAS, 442, 2362, or Pawlowski et al., 2012, MNRAS, 424, 80). Thus, the accretion of sub-halos along filaments, as seen in dark matter simulations, is inconsistent with the observed satellite structures. A different explanation is required for the existence of the (co-orbiting) satellite planes. This might be a reason for the apparent conflict of your results and the filamentary
